How crisis affect the low-income and high-income economies differently

### 2024-04-16 paper/paper.qmd
Fixing typos

\begin{align}
\text{gni\_per\_cap} &= \alpha + \beta_1 \times \text{gdp\_growth}_i + \beta_2 \times \text{population}_i + \beta_3 \times \text{unem\_rate}_i + \beta_4 \times \text{lf\_par\_rate}_i \\
&\quad + \beta_5 \times \text{trade\_per}_i + \beta_6 \times \text{inflation}_i, \\
\alpha &\sim \text{Normal}(0, 2.5), \\
\beta_1 &\sim \text{Normal}(0, 2.5), \\
\beta_2 &\sim \text{Normal}(0, 2.5), \\
\beta_3 &\sim \text{Normal}(0, 2.5), \\
\beta_4 &\sim \text{Normal}(0, 2.5), \\
\beta_5 &\sim \text{Normal}(0, 2.5)
\end{align}

@@

\begin{align}
\log(\text{gni\_per\_cap}) &= \alpha + \beta_1 \times \log(\text{gdp\_growth}_i+1) + \beta_2 \times \log(\text{population}_i +1) \\ 
&\quad + \beta_3 \times \text{unem\_rate}_i + \beta_4 \times \text{lf\_par\_rate}_i \\
&\quad + \beta_5 \times \text{trade\_per}_i + \beta_6 \times \text{inflation}_i, \\
\alpha &\sim \text{Normal}(0, 2.5), \\
\beta_1 &\sim \text{Normal}(0, 2.5), \\
\beta_2 &\sim \text{Normal}(0, 2.5), \\
\beta_3 &\sim \text{Normal}(0, 2.5), \\
\beta_4 &\sim \text{Normal}(0, 2.5), \\
\beta_5 &\sim \text{Normal}(0, 2.5)
\end{align}

>>>>

\begin{align}
\text{gni\_per\_cap} &= \alpha + \beta_1 \times \text{gdp\_growth}_i + \beta_2 \times \text{population}_i + \beta_3 \times \text{unem\_rate}_i + \beta_4 \times \text{lf\_par\_rate}_i \\
&\quad + \beta_5 \times \text{trade\_per}_i + \beta_6 \times \text{inflation}_i
\end{align}

@@

\begin{align}
\log(\text{gni\_per\_cap}) &= \alpha + \beta_1 \times \log(\text{gdp\_growth}_i+1) + \beta_2 \times \log(\text{population}_i +1) \\ 
&\quad + \beta_3 \times \text{unem\_rate}_i + \beta_4 \times \text{lf\_par\_rate}_i \\
&\quad + \beta_5 \times \text{trade\_per}_i + \beta_6 \times \text{inflation}_i
\end{align}
